Changes to police demand in COVID-19 pandemic

### 2022-03-21 docs/backup_bc_comments.Rmd
updated slides for N8 webinar

p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p4 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 4") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

@@

---
# Call types

- Quiet roads
- Expressions of concern
- Calls for advice
- Presence of guardians and absence of targets
- Violence drop
- No change in domestic violence

---
# Police response

- Higher % attended (denominator?)
- Faster response time
- Less time on scene

---
# Change in nature of demand

- For ASB the caller "profile" changed
- Otherwise no change

@@

- Further spatiotemporal analysis
- Share good practice (e.g. FHQ information to clarify rules and regulations)
- Further and more robust look at changes to domestic incidents
- Consider efficiencies (reduced time on scene)

>>>>

p1 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 1") + 
  labs(subtitle = "", caption = "", x = NULL, fill = NULL) + 
  guides(fill="none")
p2 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 2") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")
p3 <- forecast_chart(attended_by_grade_forecast,"initial_grade_of_response", "Grade 3") + 
  labs(subtitle = "", caption = "", x = NULL, y = NULL, fill = NULL) + 
  guides(fill="none")

gridExtra::grid.arrange(p1, p2, p3, ncol = 2)

@@

Highlights:

- Expressions of concern
- Calls for advice
- Violence drop
- No change in domestic violence
- For ASB the caller "profile" changed

For more (quiet roads, absence of potential victims, presence of guardians, changes in police response) please see the full report: []()

@@

- Further spatiotemporal analysis
- Share good practice (e.g. FHQ information to clarify rules and regulations)
- Further and more robust look at changes to domestic incidents

# Further training outputs

- [UKDS webinar: an introduction to time series analysis and forecasting](https://ukdataservice.ac.uk/events/an-introduction-to-time-series-analysis-and-forecasting-2/)
- A co-developed series for analysts using R and Python
